Bayesian Neural Networks

### 2024-03-25 Paper/paper.tex
Updated presentation

@@

Merkle Trees are a component of several projects, as such many papers provide incremental changes towards certain operations on Merkle trees. This paper references the original patent by Ralph Merkle \cite{merkle-patent} in addition to descriptions of Merkle tree operations given by Boneh and Shoup \cite{boneh2020graduate}. As secondary sources, the implementation of Merkle trees in Bitcoin \cite{friedenbach_alm_2017} provides a real example of the impact of hash functions in addition to a whitepaper from the BitTorrent project\cite{bep30}.

\section{Construction}
 Merkle trees are constructed from the bottom up by hashing data as the leaf nodes.

 \begin{algorithm}[H]
 	\caption{Merkle tree construction}
 	\begin{algorithmic}
 		\For{$i = 1,\ldots, n$} \Comment{Compute leaf node hashes}
 		\State $y_i \leftarrow h(x_i)$  
 		\EndFor
 		 \For{$j= 1,\ldots, n-1$}  \Comment{Compute intermediate Nodes from $y_{n+1}, \ldots , y_{2n -1}$}
 		\State $y_{i+n} \leftarrow h(y_{2i-1}, y_{2i}) $ \Comment{Hash leaf nodes below for new hash}
 		\EndFor
 		\State \Return $Y$ \Comment{Return tree where $y_{2n-1}$ is the root}
 	\end{algorithmic}
 \end{algorithm}

When referring to the parts of a Merkle tree the most common terminology is "root hash" which refers to the hashed value of the root of the tree and "leaf hash" which refers to the hash for a given data block.

@@

We used the Cifar 10....

>>>>

Neural networks....

\subsection{Convolutional Neural Networks }

Convolutional neural networks are a type of neural network that is better suited for

@@

@@

We use a bayesian convolutional neural network implementation from \href{https://github.com/kumar-shridhar/PyTorch-BayesianCNN}{Github} based on work from ... \cite{shridhar2019comprehensive} \cite{shridhar2018uncertainty}
